The Rheumatoid Arthritis data  \nSupplementary File for  \n`Detection of Epistatic Interactions in High-Dimensional Genomic Data Using Random Forests`

### 2025-07-02 Supplementary_Files/Supplementary_File_Rheumatoid_Data.Rmd
added Supplementary_Files and bib items

---
title: "The Rheumatoid Arthritis data  \nSupplementary File for  \n`Detection of Epistatic Interactions in High-Dimensional Genomic Data Using Random Forests`"
author: "Hawlader Al-Mamun,  Rob Dunne"
date: "Wednesday, September 25, 2024"
output: 
    bookdown::pdf_document2:
     toc: true
     toc_depth: 3
     fig_caption: yes
     citation_package: biblatex
bibliography: 
header-includes:
  \usepackage{dcolumn}
  \usepackage{placeins}
  \usepackage{float}
  \usepackage{biblatex}
  \usepackage{caption}
  \usepackage{subcaption}
---

@@

```{r RFlocalfdr, eval=TRUE, echo=FALSE, fig.cap='RFlocalfdr analysis',  fig.align = 'center', out.width = '50%'}
knitr::include_graphics("./supp_figs/RFlocalfdr.png")

@@

```{r hotspot, eval=TRUE, echo=FALSE, fig.cap='There is a hotspot in chromosome 6',  fig.align = 'center', out.width = '50%'}
knitr::include_graphics("./supp_figs/hotspot.png")

@@

```{r zigplogscaleextended, eval=TRUE, echo=FALSE, fig.cap='empiricalzip fitted ZIPG',  fig.align = 'center', out.width = '50%'}
knitr::include_graphics("./supp_figs/zigp_log_scale_extended.png")

@@

```{R, zipfplot, echo=FALSE, eval=TRUE, fig.cap="Zero Inflated Power Law (Zipf) Distribution", out.width = '50%',fig.align = 'center'}
knitr::include_graphics("./supp_figs/ZI_Zipf_plot.png")
```

```{R, zigpplot, echo=FALSE, eval=TRUE, fig.cap="Zero Inflated Generalized Poisson", out.width = '50%',fig.align = 'center'}
knitr::include_graphics("./supp_figs/ZIGP_plot.png")
```

```{R, zinbplot, echo=FALSE, eval=TRUE, fig.cap="Zero Inflated Negative Binomial", out.width = '50%',fig.align = 'center'}
knitr::include_graphics("./supp_figs/ZINB_plot.png")
```

@@

```{R, powerlaw, echo=FALSE, eval=TRUE, fig.cap="Plot of log(frequency) vs log(count). A power law would show a straight line", out.width = '50%',fig.align = 'center'}
knitr::include_graphics("./supp_figs/power_law.png")
```

>>>>

---
title: "The Rheumatoid Arthritis data  \nSupplementary File for  \n`Detection of Epistatic Interactions in High-Dimensional Genomic Data Using Random Forests`"
author: "Hawlader Al-Mamun,  Rob Dunne"
date: "Wednesday, September 25, 2024"
output: 
    bookdown::pdf_document2:
     toc: true
     toc_depth: 3
     fig_caption: yes
     citation_package: biblatex
bibliography: 
    ../epistaticInteractions.bib 
header-includes:
  \usepackage{dcolumn}
  \usepackage{placeins}
  \usepackage{float}
  \usepackage{biblatex}
  \usepackage{caption}
  \usepackage{subcaption}
---

@@

```{r RFlocalfdr, eval=TRUE, echo=FALSE, fig.cap='RFlocalfdr analysis',  fig.align = 'center', out.width = '50%'}
knitr::include_graphics("RFlocalfdr.png")

@@

```{r hotspot, eval=TRUE, echo=FALSE, fig.cap='There is a hotspot in chromosome 6',  fig.align = 'center', out.width = '50%'}
knitr::include_graphics("hotspot.png")

@@

```{r zigplogscaleextended, eval=TRUE, echo=FALSE, fig.cap='empiricalzip fitted ZIPG',  fig.align = 'center', out.width = '50%'}
knitr::include_graphics("zigp_log_scale_extended.png")

@@

```{R, zipfplot, echo=FALSE, eval=TRUE, fig.cap="Zero Inflated Power Law (Zipf) Distribution", out.width = '50%',fig.align = 'center'}
knitr::include_graphics("ZI_Zipf_plot.png")
```

```{R, zigpplot, echo=FALSE, eval=TRUE, fig.cap="Zero Inflated Generalized Poisson", out.width = '50%',fig.align = 'center'}
knitr::include_graphics("ZIGP_plot.png")
```

```{R, zinbplot, echo=FALSE, eval=TRUE, fig.cap="Zero Inflated Negative Binomial", out.width = '50%',fig.align = 'center'}
knitr::include_graphics("ZINB_plot.png")
```

@@

```{R, powerlaw, echo=FALSE, eval=TRUE, fig.cap="Plot of log(frequency) vs log(count). A power law would show a straight line", out.width = '50%',fig.align = 'center'}
knitr::include_graphics("power_law.png")
```
